-   <div>

    ---
    title: "DANL 200: Introduction to Data Analytics<br>Project"
    subtitle: "Quarto Template<br><br>" 
    author: 
      - name: Bailey
        affiliations:
          - SUNY Geneseo
      - name: Josh
        affiliations:
          - SUNY Geneseo
      - name: Marcus
        affiliations:
          - SUNY Geneseo
      - <br>
    date: "`r Sys.Date()`"

    format: 
      html:
        toc: true
        number-sections: true
        code-fold: false      
        code-summary: "Show the code"
        code-tools: true
        highlight-style: espresso # 

    execute: 
      echo: true
      eval: true
      warning: false
      message: false
      fig-width: 9
    ---

    </div>

```{r setup, include = FALSE}
library(tidyverse)

path <- 'https://bcdanl.github.io/data/climate_finance_energy.csv'
climate_finance <- read_csv(path)

library(skimr)

```

```{r}
BS <- read_csv('https://bcdanl.github.io/data/climate_finance_energy.csv')
nvars <- format(round(ncol(BS), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(BS), 0), 
                nsmall=0, 
                big.mark=",")
```

-   Here is the paged table using `rmarkdown::paged_table()`. Each country in the "party" category is the country that is providing the aid to the recipient country

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(BS) 
```

<br>

The number of variables is `r nvars`; the number of observations is `r nobs`.

<br>

# Introduction

This project is going to be used for our DANL 200 course. The primary reason our project matters would be to showcase how over the semester we have learned how to code and this is the final "test" in a sense of what we have learned to do.The data set we choose to use for this project address relations between other countries and showcases which countries provide aid to other countries. In this project, these questions will be covered.

-which country provides the most support

-which country provides the least support

-why this subject matters

-is there a correlation between where a country is and why it may contribute more to other countries

-   

# Data

## Data Summary

1.  **Party**

    -   Count: 3

    -   Unique Values: 2

2.  **Recipient Country/Region**

    -   Count: 3

    -   Unique Values: 2

3.  **Project/Program/Activity**

    -   Count: 1

    -   Unique Values: 1

4.  **Type of Support**

    -   Count: 3

    -   Unique Values: 1

5.  **Year**

    -   Count: 3

    -   Mean: 2015.67

    -   Standard Deviation: 1.15

    -   Min: 2015

    -   25th Percentile: 2015

    -   Median (50th Percentile): 2015

    -   75th Percentile: 2016

    -   Max: 2017

6.  **Contribution**

    -   Count: 3

    -   Mean: 13,495.39

    -   Standard Deviation: 3,209.92

    -   Min: 11,074.20

    -   25th Percentile: 11,674.88

    -   Median (50th Percentile): 12,275.56

    -   75th Percentile: 14,705.99

    -   Max: 17,136.41

7.  **Status**

    -   Count: 3

    -   Unique Values: 1

8.  **Energy**

    -   Count: 3

    -   Unique Values: 1

## Data Visualization

```{r}
ggplot(BS, aes(x = Contribution)) +
  geom_histogram(bins = 100,
                 fill = "blue", 
                 color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Contributions",
       x = "Contribution",
       y = "Frequency")

 
```

## Data Transformation

```{r}
climate_finance_transformed <- climate_finance %>%
  mutate(
    Year = as.factor(Year),
    Contribution_Normalized = scales::rescale(Contribution, to = c(0, 1)),
    Energy_Encoded = as.numeric(Energy),
    Contribution_Category = cut(Contribution, 
                                breaks = c(-Inf, 10000, 50000, Inf), 
                                labels = c('Low', 'Medium', 'High')),
    Year_Group = ifelse(Year <= 2010, 'Before 2010', 
                        ifelse(Year <= 2015, '2011-2015', 'After 2015'))
  )

head(climate_finance_transformed)


```

```{r}
total_contributions <- aggregate(Contribution ~ Party, data = climate_finance, sum)

least_contributing_country <- total_contributions[which.min(total_contributions$Contribution), ]

print(least_contributing_country)
```

```{r}
total_contributions <- aggregate(Contribution ~ Party, data = climate_finance, sum)

most_contributing_country <- total_contributions[which.max(total_contributions$Contribution), ]

print(most_contributing_country)


```

## explanation of the data and website

Overall this project has been a huge eye-opening experience regarding the difficulty and meticulous efforts to set up a website and code. This data.frame that I have discussed has a very significant importance when it comes to how other countries give aid to others. Countries all over the world have allies. Whether it may be the United States or Russia, but a way to keep in good standing with you're allies or even countries you may what to become allies or good friends with is aid. So this data set showcases which countries are helping each other the most and which ones are not helping certain countries.

The most contributions made by anyone would be the EU which would make the most amount of sense considering its a group configured of lots of other countries, but they singulary have contributed the most other than any other organization or country

The least amount of contributions made by anyone would be Monaco. Monaco is the second smallest indapendant state in the world so it makes the most sense why it would contribute the least if any at all.

<br><br><br><br>

# References

-   <https://quarto.org/docs/output-formats/html-basics.html>

-   <https://quarto.org/docs/websites/>
